A thesis draft

### 2018-09-19 draft.tex
Add Docker Swarm software description

\paragraph{Docker Swarm} \todo{Talk about its characteristic and introduce it}

\vspace{0.5cm}

>>>>

\paragraph{Docker Swarm} Introduced in ??\todo{Find Docker Swarm date of
birth}, Docker Swarm allows multiple Docker nodes to cluster together and be
seen as one logical unit. This layer completely makes the underlying
infrastructure transparent: data management, as network one, are totaly managed
by Docker. Recently, Docker-compose support has been introduced, making
this one-node tool available for clustered systems. At the end of the day, on
one hand Docker Swarm provides an easy way to set up a cluster system with all
the tools configured out-of-the-box, without the necessity to set networking
configurations or installing ad-hoc storage solutions. On the other hand,
though, it doesn't have all the personalization options that Kuberentes offers,
thus making the product less flexible. This foundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs.
\vspace{0.5cm}
